### 2023-04-11 article.tex
Improve definition of paradata

{\bf Keywords:} paradata, reproducible research, code, software,
FAIR data, computational research, Open Science, best practices,
genetic epidemiology

@@

This paper defines paradata as 'data about the data collection 
process' (\cite{choumert2019using}).
This definition is chosen for its simplicity, 
yet there are multiple related and/or more nuanced 
definitions of paradata (see for example \cite{huvila2022improving} 
and \cite{skold2022interrogating}).

@@

One problem that containers have, is their size:
they can be several gigabytes big. 
This makes the distribution of these containers harder.
Ideally, containers are stored online and distributed in
standardised ways.
Although progress is being made, 
there is no way to do so for all container types.
Additionally, probably due to their novelty,
container hosting sites lack metadata.

>>>>

{\bf Keywords:} paradata, reproducible research, code, software,
computational research, Open Science, best practices,
genetic epidemiology

@@

There exists no standard definition of paradata (\cite{nicolaas2011survey,skold2022interrogating,huvila2022improving}).
Without declaring it a formal definition, however,
paradata is 'data about processes' (and example survey paradata 
are call records and audit trails) \cite{nicolaas2011survey},
or 'data about the data collection process' (\cite{choumert2019using}).
This paper uses the latter as a working definition.

@@

Containers do have problems.
First, they themselves require software to run,
with the same software decay being possible.
Second, one needs to install that software and have the
computer access rights (i.e. admin rights under Windows, 
or root rights under Linux) to do so.
Third, one needs to learn how to build and use containers.
Lastly, containers can be several gigabytes big files,
which makes their distribution harder.
Ideally, containers are stored online and distributed in
standardised ways.
Although progress is being made, 
there is no way to do so for all container types.
Additionally, probably due to their novelty,
container hosting sites lack metadata.
